Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-08-19 manuscript/manuscript.tex
changed brownian bridge notation

Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
case where $\theta$ is known.  Note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \theta_0)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0)),
\end{equation*}
where $\theta_0$ is the true parameter value of $\theta$ under~$H_0$.
When $\hat\theta_n$ is replaced with $\theta_0$, as in the standard KS testing
situation, the second term vanishes, and $T_n$ converges in distribution to that
of $\sup_t | B(F(t; \theta_0)) |$, where $B(\cdot)$ is the standard Brownian bridge
\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
second term leads to a bias in the Brownian bridge, which was addressed by
\citet{babu2004goodness}.

>>>>

Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
case where $\theta$ is known.  Note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \theta_0)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0)),
\end{equation*}
where $\theta_0$ is the true parameter value of $\theta$ under~$H_0$.
When $\hat\theta_n$ is replaced with $\theta_0$, as in the standard KS testing
situation, the second term vanishes, and $T_n$ converges in distribution to that
of $\sup_t | J(F(t; \theta_0)) |$, where $J(\cdot)$ is the standard Brownian bridge
\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
second term leads to a bias in the Brownian bridge, which was addressed by
\citet{babu2004goodness}.
